Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-18 doc/GMP2015/s05_problems.tex
Citation added to Section 5

The \dfn{restricted optimal DR-planning problem} requires DR-plans of
one of these types, which reduces to recognizing if the input graph is
a 2-tree or a tree-decomposable graph for which simple near-linear
time algorithms are available \uncited and the DR-plan is a
by-product output of the recognition algorithm.

In the recombination setting, the corresponding \dfn{restricted
OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic
completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction}
or to be a low Cayley complexity tree-decomposable graph as in Section
\ref{sec:tdecomp}. Clearly these problems have deterministic
polynomial time algorithms, the algorithms run in time exponential in
$k$. As a result, when $k$ is part of the input, the \dfn{restricted
OMD problem} has the potential to be difficult. For example, when the
isostatic completion $H$ is required to be a 2-tree the restricted OMD
problem is reducible to the maximum spanning series-parallel subgraph
problem shown by \uncited\uncited to be NP-complete even if the input
graph is planar of maximum degree at most 6. However, since the OMD
problem has other input restrictions such as not having any proper
isostatic subgraphs, it is not clear if the reverse reduction exists
and hence it is unclear whether the OMD problem is NP-complete. The
same holds for the restricted OMD problem where the isostatic
completion $H$ is required to be a tree-decomposable graph of low
Cayley complexity (i.e, have special, small DR-plans). One potential
obstacle to an indecomposable graph $G$'s membership in the restricted
OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth.
In fact, 6-connected (hence rigid) graphs with arbitrarily large girth
have been constructed in \uncited.
%
\subsection{Optimal Modification, Completion and Recombination: formal
connections}
%
The OMD problem is closely related to a well-studied problem of
completion of an under-constrained system to an isostatic one with a
small DR-plan.
\begin{observation}
    The (decision version of) the {\bf optimal completion problem
    (OC)} from \cite{bib:survey, j-a, fang} is OMD$_0$.
\end{observation}.
In fact, a \dfn{restricted OC} problem was studied by \cite{j-a}
requiring the completion to be tree-decomposable. It is not clear if
the reverse reduction holds, i.e, is OMD reducible to OC?

>>>>

The \dfn{restricted optimal DR-planning problem} requires DR-plans of
one of these types, which reduces to recognizing if the input graph is
a 2-tree or a tree-decomposable graph for which simple near-linear
time algorithms are available \cite{valdes1979recognition,fudos1997graph} and the DR-plan is a
by-product output of the recognition algorithm.

In the recombination setting, the corresponding \dfn{restricted
OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic
completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction}
or to be a low Cayley complexity tree-decomposable graph as in Section
\ref{sec:tdecomp}. Clearly these problems have deterministic
polynomial time algorithms, the algorithms run in time exponential in
$k$. As a result, when $k$ is part of the input, the \dfn{restricted
OMD problem} has the potential to be difficult. For example, when the
isostatic completion $H$ is required to be a 2-tree the restricted OMD
problem is reducible to the maximum spanning series-parallel subgraph
problem shown by \cite{cai1993spanning} to be NP-complete even if the input
graph is planar of maximum degree at most 6. However, since the OMD
problem has other input restrictions such as not having any proper
isostatic subgraphs, it is not clear if the reverse reduction exists
and hence it is unclear whether the OMD problem is NP-complete. The
same holds for the restricted OMD problem where the isostatic
completion $H$ is required to be a tree-decomposable graph of low
Cayley complexity (i.e, have special, small DR-plans). One potential
obstacle to an indecomposable graph $G$'s membership in the restricted
OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth.
In fact, 6-connected (hence rigid) graphs with arbitrarily large girth
have been constructed in \cite{servatius2000rigidity}.
%
\subsection{Optimal Modification, Completion and Recombination: formal
connections}
%
The OMD problem is closely related to a well-studied problem of
completion of an under-constrained system to an isostatic one with a
small DR-plan.
\begin{observation}
    The (decision version of) the {\bf optimal completion problem
    (OC)} from \cite{bib:survey, j-a, fang} is OMD$_0$.
\end{observation}
In fact, a \dfn{restricted OC} problem was studied by \cite{j-a}
requiring the completion to be tree-decomposable. It is not clear if
the reverse reduction holds, i.e, is OMD reducible to OC?
